Fig2: Candidate genes

### 2020-05-31 analysis/figure-2.Rmd
now colors, include control for fig 2

---
title: "Fig2: Candidate genes"
author: "Rayna M Harris"
date: "3/26/2020"
output: md_document
---

@@

```{r candidatevsds}
# load `candidatevsd` with `source("../R/wrangledata.R")`
candidatevsd <- read_csv("../results/03_candidatevsd.csv") %>% 
  select(-X1) %>%
  filter(treatment %in% charlevelsnocontrol) %>%
  drop_na()
tail(candidatevsd)

@@

@@

  p <- candidatevsd %>%
    filter(tissue %in% whichtissue,
           gene %in% whichgenes,
           sex %in% whichsex) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    ggplot(aes(x = treatment, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    #facet_wrap(~sex,  nrow = 1) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          axis.title.y = element_text(face = "italic"),
          axis.text.x = element_blank(),
          axis.ticks = element_blank(),
          axis.line.x = element_blank()) +
    labs(y = whichgenes,
         x = NULL) +
    geom_signif(comparisons = list( c( "bldg", "lay"),
                                   c( "lay", "inc.d3"),
                                   c("inc.d3", "inc.d9"),
                                   c( "inc.d9", "inc.d17"),
                                   c( "inc.d17", "hatch"),
                                   c("hatch", "n5"),
                                   c( "n5", "n9")),  
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0.2)

@@

c1 <- scattercorrelations(FH, FH$CRHR2, "CRHR2", FH$HTR2C, "HTR2C", "#969696" ) +  labs(title = " ", subtitle = " " )  
c3 <- scattercorrelations(FP, FP$AVPR1A, "AVPR1A", FP$CRHR1,  "CRHR1", "#969696")  + labs(title = " ", subtitle = " ") 
c5 <- scattercorrelations(FG, FG$CRHBP, "CRHBP",  FG$ESR2,  "ESR2", "#969696")   + labs(title = " ", subtitle = " ")

c2 <- scattercorrelations(MH, MH$DRD1, "DRD1", MH$HTR2C, "HTR2C", "#525252")  + labs(title = " ", subtitle = " " )  
c4 <- scattercorrelations(MP, MP$AVPR1A,  "AVPR1A",  MP$CRHR1, "CRHR1", "#525252")  + labs(title = " ", subtitle = " " ) 
c6 <- scattercorrelations(MG, MG$PGR, "PGR", MG$PRLR, "PRLR", "#525252")   + labs(title = " ", subtitle = " " )

d1 <- candidateboxplot("hypothalamus", c("CRHR2"), "female") + labs(x = NULL, title =  "Hypothlamic expression", subtitle = "females" )  
d2 <- candidateboxplot("hypothalamus", c("HTR2C"), "female") + labs(x = NULL )  + theme(axis.text.x = element_text(angle = 45, vjust = 1))
d3 <- candidateboxplot("pituitary", c("AVPR1A"), "female") + labs(x = NULL , title = "Pituitary expression", subtitle = "females") 
d4 <- candidateboxplot("pituitary", c("CRHR1"), "female") + labs(x = NULL  )  + theme(axis.text.x = element_text(angle = 45, vjust = 1))
d5 <- candidateboxplot("gonad", c("CRHBP"), "female") + labs(x = NULL, title = "Gonadal expression", subtitle = "females")
d6 <- candidateboxplot("gonad", c("ESR2"), "female") + labs(x = NULL ) + theme(axis.text.x = element_text(angle = 45, vjust = 1))

e1 <- candidateboxplot("hypothalamus", c("DRD1"), "male") + labs(x = NULL, title = " " , subtitle = "males" )  
e2 <- candidateboxplot("hypothalamus", c("HTR2C"), "male") + labs(x = NULL )  + theme(axis.text.x = element_text(angle = 45, vjust = 1))
e3 <- candidateboxplot("pituitary", c("AVPR1A"), "male") + labs(x = NULL , subtitle = "males" ) 
e4 <- candidateboxplot("pituitary", c("CRHR1"), "male") + labs(x = NULL  )  + theme(axis.text.x = element_text(angle = 45, vjust = 1))
e5 <- candidateboxplot("gonad", c("PGR"), "male") + labs(x = NULL, subtitle = "males" ) 
e6 <- candidateboxplot("gonad", c("PRLR"), "male") + labs(x = NULL )   + theme(axis.text.x = element_text(angle = 45, vjust = 1))

@@

pdf(file="../figures/fig2-1.pdf", width=7.25, height=7.25)
plot(fig2)
dev.off()
```

```{r writefiles}
#write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")
#write.csv(candidatevsd, "../results/candidatecounts.csv")
write.csv(table1, "../results/table1.csv")
```

>>>>

---
title: "Fig2: Candidate genes"
output: md_document
---

@@

```{r candidatevsds}
# load `candidatevsd` with `source("../R/wrangledata.R")`
candidatevsd <- read_csv("../results/03_candidatevsd.csv") %>% 
  select(-X1) %>%
  filter(treatment %in% charlevels) %>%
  drop_na()
head(candidatevsd)

@@

```

@@

  p <- candidatevsd %>%
    filter(tissue %in% whichtissue,
           gene %in% whichgenes,
           sex %in% whichsex) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    ggplot(aes(x = treatment, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    #facet_wrap(~sex,  nrow = 1) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          axis.title.y = element_text(face = "italic"),
          axis.text.x = element_blank(),
          axis.ticks = element_blank(),
          axis.line.x = element_blank()) +
    labs(y = whichgenes,
         x = NULL) +
    geom_signif(comparisons = list( c( "control", "bldg"),
                                    c( "bldg", "lay"),
                                   c( "lay", "inc.d3"),
                                   c("inc.d3", "inc.d9"),
                                   c( "inc.d9", "inc.d17"),
                                   c( "inc.d17", "hatch"),
                                   c("hatch", "n5"),
                                   c( "n5", "n9")),  
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0.2)

@@

c1 <- scattercorrelations(FH, FH$DRD1, "DRD1", FH$HTR2C, "HTR2C", "#969696" ) +  labs(title = " ", subtitle = " " )  
c3 <- scattercorrelations(FP, FP$AVPR1A, "AVPR1A", FP$CRHR1,  "CRHR1", "#969696")  + labs(title = " ", subtitle = " ") 
c5 <- scattercorrelations(FG, FG$PGR, "PGR",  FG$ESR1,  "ESR1", "#969696")   + labs(title = " ", subtitle = " ")

c2 <- scattercorrelations(MH, MH$DRD1, "DRD1", MH$HTR2C, "HTR2C", "#525252")  + labs(title = " ", subtitle = " " )  
c4 <- scattercorrelations(MP, MP$AVPR1A,  "AVPR1A",  MP$CRHR1, "CRHR1", "#525252")  + labs(title = " ", subtitle = " " ) 
c6 <- scattercorrelations(MG, MG$PGR, "PGR", MG$ESR1, "ESR1", "#525252")   + labs(title = " ", subtitle = " " )

d1 <- candidateboxplot("hypothalamus", c("DRD1"), "female") + labs(x = NULL, title =  "Hypothlamic expression", subtitle = "females" )  
d2 <- candidateboxplot("hypothalamus", c("HTR2C"), "female") + labs(x = NULL )  + theme(axis.text.x = element_text(angle = 45, vjust = 1))
d3 <- candidateboxplot("pituitary", c("AVPR1A"), "female") + labs(x = NULL , title = "Pituitary expression", subtitle = "females") 
d4 <- candidateboxplot("pituitary", c("CRHR1"), "female") + labs(x = NULL  )  + theme(axis.text.x = element_text(angle = 45, vjust = 1))
d5 <- candidateboxplot("gonad", c("PGR"), "female") + labs(x = NULL, title = "Gonadal expression", subtitle = "females")
d6 <- candidateboxplot("gonad", c("ESR1"), "female") + labs(x = NULL ) + theme(axis.text.x = element_text(angle = 45, vjust = 1))

e1 <- candidateboxplot("hypothalamus", c("DRD1"), "male") + labs(x = NULL, title = " " , subtitle = "males" )  
e2 <- candidateboxplot("hypothalamus", c("HTR2C"), "male") + labs(x = NULL, title = " " )  + theme(axis.text.x = element_text(angle = 45, vjust = 1))
e3 <- candidateboxplot("pituitary", c("AVPR1A"), "male") + labs(x = NULL , subtitle = "males", title = " " ) 
e4 <- candidateboxplot("pituitary", c("CRHR1"), "male") + labs(x = NULL, title = " "  )  + theme(axis.text.x = element_text(angle = 45, vjust = 1))
e5 <- candidateboxplot("gonad", c("PGR"), "male") + labs(x = NULL, subtitle = "males", title = " " ) 
e6 <- candidateboxplot("gonad", c("ESR1"), "male") + labs(x = NULL , title = " ")   + theme(axis.text.x = element_text(angle = 45, vjust = 1))

@@

```

```{r writefiles}
#write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")
#write.csv(candidatevsd, "../results/candidatecounts.csv")
write.csv(table1, "../results/table1.csv")

pdf(file="../figures/fig2-1.pdf", width=7.25, height=7.25)
plot(fig2)
dev.off()
